Untitled

### 2018-07-17 PaperCode.Rmd
High value LUPS
I added in the number of LUPS that are worth more than the LAD median. This required changing BootsratpDistribcompare. However I can now predict the LADs where the majority of LUPs are high value, which is easier for people to understand.

BirminghamDATA <-  read_excel("Birmingham CT EMPTIES.xlsx" )%>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Current Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
  StructureData()

@@

#Mid Suffolk and Babergh
#These have been combined and are just the postcodes so need to be fixed
#Missing loads of postcodes
MidSuffolkDATA <- read_excel("MidSuffolk FOI MF379 1718 Discount.xlsx") %>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
  StructureData(c(2:12,14:15))

BaberghDATA <- read_excel("Babergh FOI BF378 1718 Discount.xlsx")%>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
  StructureData(c(2:6,8:11,13:15))

@@

#Wandsworth

# WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
#   group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
#   arrange(`Ptc Wardname`) %>% 
#   filter(!is.na(`Ptc Wardname`)) %>% 
#   bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
#               select(Admin_ward_code)) %>%
#   mutate(LowUse = Empty) %>%
#   SemiDataStructure
# 
# 
# #Kingston
# 
# KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
#   arrange(X__1) %>% slice(1:16) %>%
#   bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
#               select(Admin_ward_code)) %>%
#   mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
#   SemiDataStructure

@@

PlotMap(WandsworthLONDDATA)

@@

@@

decile %>% 
  filter(type == "Including London") %>% 
  ggplot(aes(x= ratio, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")

@@

data_frame(Index = 1:100) %>%
  mutate(Primary = exp(-0.05*(Index))+0.05, 
         Auxilary = (exp(Index/100)-1),
    Total = Primary + Auxilary) %>%
  gather(key = "Type", value = "value", -Index) %>%
  ggplot(aes(x= Index, y = value, colour = Type )) +
  geom_point() +
  labs(title = "LUP percentage as a function of primary and Auxilary demand",
       x = "Demand",
       y = "LUP percentage") +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank()
  )
SaveFig("TheoreticalDemand.pdf")

@@

setwd(basewd)

BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
                                         PropertyTypes = c("D", "S", "T", "F"))

elementnames<- names(BootStrapRESExO)

#Used when elements need to be deleted and reloaded
#saveRDS(BootStrapRESExO, "BootStrapRESExO.rds")

#Make a summary dataframe
Combine1ExO <- BootResSummaryData(BootStrapRESExO) 
```

@@

test <- BootStrapRESExO %>% 
  bind_rows %>%
  group_by(class, ID) %>%
  summarise_all(sum) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")),
               LUPmore = RatioExvsAct>1)

@@

BootStrapRESExO2 <- BootStrapRESExO %>% map(~.x %>% ungroup)

@@

LUPval <-   map2(.x =BootStrapRESExO2, .y =   names(BootStrapRESExO2),~ {.x %>% mutate(LAD  = .y)}) %>%
  bind_rows %>%
  select(-class) %>%
  group_by(LAD, ID) %>%
  summarise_all(sum) %>%
  group_by(LAD) %>%
  summarise_all(mean) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
  mutate(VancouverTax = LowUseValue*0.01/1000)

LUPval$VancouverTax %>% sum(.)/1000

@@

Combine1ExO %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
  geom_jitter()

Rural Urban split
```{r}
# setwd(DataFolder)
# 
# Rural <- read_csv( "RUC11_LAD11_ENv2.csv" )[-1,] %>%
#   setNames(make.names(names(.))) %>%
#   rename(PercRural = Rural.including.hub.towns..rural...rural.related..population1_1) %>%
#   select(LAD11CD, PercRural) %>%
#   mutate(PercRural = as.numeric(PercRural))
# 
# #Update Gateshead and Northumberland Codes
# Rural$LAD11CD[Rural$LAD11CD == "E08000020"] <-"E08000037"
# Rural$LAD11CD[Rural$LAD11CD == "E06000048"] <- "E06000057"
# 
# Combine1ExO <- Combine1ExO %>%
#   left_join(Rural, by = "LAD11CD")

@@

@@

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
#  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
#  left_join(Rural, by = "LAD11CD") %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent),
         LUPdepExt = scale(LUPdepExt),
         maxPerc = scale(maxPerc),
         VacantsPerc = scale(VacantsPerc),
         price = scale(price),
         Extent = scale(Extent))

#This uses the local mean so that has to be run first before the code works
# ModelMe <- Combine1ExO2 %>%
#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
#   #filter out wales
#   filter(!grepl("W", LAD11CD))%>%
#   select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value,  LAD11CD) %>%
#   mutate(outcome = LUPdepExt>Extent)  %>% 
#   left_join(LocalMean, by = "LAD11CD") %>%
#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
#   mutate(priceRatio = (price/LocalMean)) %>%
#   mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price-LocalMean ) %>%
#   #make the Reference column properly
#   mutate(Reference = as.factor(absdiff>0) ) %>%
#   #scaled so that the binomial can be interpreted
#   mutate(pricepercent = scale(pricepercent),
#          LUPdepExt = scale(LUPdepExt),
#          maxPerc = scale(maxPerc),
#          priceRatio = scale(priceRatio))

ModelMe %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
  geom_jitter()

rowsum(.)>5 ~TRUE
#classification

#LUPdepExt and Pricepercent are the only useful ones really
Binom <- glm(Reference~ LUPdepExt +LADPerc +maxPerc+ mean.y, family=binomial(link='logit'),data=ModelMe)

Binom <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)

confusionMatrix(predict(Binom, ModelMe, type = "response")>0.5 , ModelMe$Reference)

test <- lm(Percdiff ~ LUPdepExt +LADPerc +maxPerc+ mean.y, data = ModelMe)

summary(Binom)

coef(Binom) %>% as.data.frame
```

##perform many mode resamples and plot the results

#binom

set.seed(1983)
ModelStats <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
                              as.data.frame(TestResample$test)$Reference)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

test <- ModelStats %>% 
  select( X.Intercept., LUPdepExt, price, VacantsPerc) %>%
  gather

test %>% ggplot(.,aes(x = key, y = value, fill = key)) + geom_boxplot() + 
  labs(title = "Direction each variable pushes the outcome")

test %>% ggplot(.,aes(x = value, fill = key)) + geom_density( alpha = 0.5)

@@

```{r}
set.seed(1983)
ModelStats2 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ Extent + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
                              as.data.frame(TestResample$test)$Reference)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

set.seed(1983)
ModelStats3 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
                              as.data.frame(TestResample$test)$Reference)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

Outcome <- bind_rows(data_frame(model = "Open Data", Accuracy = ModelStats2$Accuracy), 
data_frame(model = "cutsom", Accuracy = ModelStats3$Accuracy) )

Outcome %>%
  ggplot(.,aes(x = Accuracy, fill = model)) + geom_density(alpha = 0.3) +
  labs(title = "Density plot of the model outcomes, using custom FOI data vs generic open data")
SaveFig("CustomGenericOutcomes.pdf")

#The model that uses easily available data is 3% less accurate than the other model.
t.test(ModelStats2$Accuracy, ModelStats3$Accuracy)

cor(ModelMe$Vacants, ModelMe$VacantsPerc)

cor(ModelMe$Vacants, ModelMe$LTV)
cor(ModelMe$VacantsPerc, ModelMe$LTVPerc)

#Plot the model coefficients

ModelStats2 %>%
  select(X.Intercept. ,Extent,price , VacantsPerc) %>%
  gather() %>%
  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
  labs(title = "Coefficient values across 1000 random partitions")
SaveFig("ModelCoeffs.pdf")

#only one of these is necessary they hold almost the same information
ModelStats3 %>%
  select(X.Intercept. ,LUPdepExt,price , VacantsPerc) %>%
  gather() %>%
  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
  labs(title = "Coefficient values across 1000 random partitions")

@@

interpreting the coefficients of the model shows us that there is a natural tendency for LUPs to be more expensive than regular housing, the probability of them being more expensive increases if the local authority is already expensive compared to the rest of the local authorities. In addition the greater the maximum concentration of LUPs also increase the probability of them being more expensive than regular housing. However if the LUPs are generally in deprived areas then the probability of them being more expensive than regular housing decreases.

Using the models produced in the previous section I can now predict areas where primary purchases are being out competed across the England

#Linear
set.seed(1983)
MultiCheckL <- 1:111 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

  model <- glm(Reference~ Extent + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample))

  data_frame(x = predict(model, ModelMe, type = "response")>0.5) %>%
    setNames(paste("Model", .x, sep="_"))
}
) %>% bind_cols() %>% mutate(
  Outcome = case_when(
  rowSums(.)>ncol(.)/2 ~TRUE,
  rowSums(.)<=ncol(.)/2 ~FALSE
))

#Tree
set.seed(1983)
MultiCheck <- 1:111 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

  model <- rpart(Reference~ Extent + 
                   price + 
                   VacantsPerc  
                 ,data=as.data.frame(TestResample))

  data_frame(x = predict(model, ModelMe, type = "prob")[,2]>0.5) %>%
    setNames(paste("Model", .x, sep="_"))
}
) %>% bind_cols() %>% 
  mutate(
  Outcome = case_when(
  rowSums(.)>ncol(.)/2 ~TRUE,
  rowSums(.)<=ncol(.)/2 ~FALSE
))

test <- ModelMe %>%
  bind_cols(., select(MultiCheck, Outcome)) %>%
  mutate(Correct = Reference == Outcome) %>%
  filter(!Correct) %>%
  select(LAD, Reference, Outcome)

confusionMatrix(MultiCheckL$Outcome, ModelMe$Reference)  
confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)

ModelMe %>% 
  mutate(Outcome = as.logical(MultiCheck$Outcome)) %>%
  filter(Outcome != Reference) %>%
  select(LAD, Outcome, Reference)

@@

tol <- 0

#random forest appears better than multilinear but when checked on many resamples it is worse... how? To much noise?
EnglandComp <- LADDep %>% 
  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
  left_join(., Vacants, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
  left_join( LadHomes, by = "LAD11CD") %>%
  #left_join(Rural, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes)

#Preds <- predict(BinomExtent, EnglandComp , type = "response")
set.seed(1983)
Preds <- 1:111 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

  model <- rpart(Reference~ Extent + price + VacantsPerc,data=as.data.frame(TestResample))

  data_frame(x = predict(model, EnglandComp, type = "prob")[,2]>0.5) %>%
    setNames(paste("Model", .x, sep="_"))
}
) %>% bind_cols() %>% 
  mutate(
  Outcome = rowSums(.)/ncol(.))

EnglandComp <- EnglandComp%>% 
  left_join(select(ModelMe, LAD11CD, Reference), by = "LAD11CD") %>%
  mutate(
    Significant.Competition = ifelse(is.na(Reference),
                                     unlist(Preds$Outcome), 
                                     as.logical(Reference))
    ) %>%
  mutate(

      Comp.Type = case_when(
      .$Significant.Competition<0.5-tol ~"No",
      .$Significant.Competition>0.5 + tol ~"Yes",
      .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
      )
  )

EnglandComp %>%
  ggplot(aes(x = Comp.Type, y= price, fill = Comp.Type)) + geom_boxplot()

#Estimated

EnglandCompTab <- EnglandComp %>%
  group_by(Comp.Type) %>%
  summarise(mean = mean(price),
            median = median(price),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes)*100,
         PopPerc = Pop/sum(Pop)*100) %>%
  rename('LUPs>Homes' = Comp.Type, 
         Population = Pop,
         'Homes %' = HomesPerc,
         'Population %' = PopPerc) %>%
  gather(key = "key", "value"= value, -"LUPs>Homes") %>%
  mutate(value = value %>% round %>%as.integer) %>%
  spread(key = "LUPs>Homes", value = value)

EnglandCompTab

xtable(EnglandCompTab, caption="Summary of effect across England",
       label = "tab:EnglandCompTab") %>% 
  print(., type="latex", file=file.path(TexTables,"EnglandCompTab.tex"))

#Observed
Combine1ExO %>%
  group_by((absdiff>0)) %>%
  summarise(mean = mean(HomePrice),
            median = median(HomePrice),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes),
         PopPerc = Pop/sum(Pop))

#Plotting the expected range of

valuecheck <- sample(c(TRUE, FALSE), size = nrow(EnglandComp)*1000, replace = TRUE, prob = c(0.888, 1-0.888)) %>%
  matrix(., nrow=nrow(EnglandComp)) 
valuecheck <-   (valuecheck * ifelse(EnglandComp$Comp.Type == "Yes", TRUE, FALSE ) )%>% data.frame %>%
  bind_cols(select(EnglandComp, LAD11CD, Reference),.) %>%
  #Where ever the outcome is known it is reverted back to the true value, only estimated values are flipped.
  gather(key = "ID", value = "affected",-LAD11CD,-Reference) %>%
  mutate(Reference = as.logical(Reference)*1,
    affected = ifelse(is.na(Reference), affected, Reference)) %>%
  left_join(LadHomes) %>%
  group_by(ID, affected) %>%
  summarise(Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  group_by(affected) %>%
  mutate(Rank = percent_rank(Pop),
    Outlier = ifelse(percent_rank(Pop)<0.0275 | percent_rank(Pop)>0.975, "Yes", "No")) %>%
  group_by(ID) %>%
  mutate(affected = ifelse(affected == 1, "Yes", "No"),
         PercPop = Pop/sum(Pop))%>%
  ungroup #%>%
# mutate(PercPop = Pop)
#The NNUMBERS DONT MATCH WITH THE TABLE WHY?

#95 range is 78 to 84
affected <- valuecheck %>% filter(affected == "Yes")
q5 <- quantile(affected$PercPop,.05)
q95 <- quantile(affected$PercPop,.95)
x.dens <- density(affected$PercPop)
df.dens <- data.frame(x = x.dens$x, y = x.dens$y)
median(affected$PercPop)
affected %>%
  ggplot(aes(x = PercPop)) + geom_density() +
  geom_area(data = subset(df.dens, x <= q5), 
              aes(x=x,y=y))  +
    geom_area(data = subset(df.dens, x >= q95), 
              aes(x=x,y=y))+
labs(title = "The estimated percentage of English population affected by LUPs")
SaveFig("PopPercLUPAfftect.pdf")

valuecheck %>% filter(affected == "No") %>%
  ggplot(aes(x = PercPop)) + geom_density()

@@

test <-ls(pattern = "DATA") %>%
  map_df(~get(.x) %>%
           group_by(LAD11CD) %>%
           mutate(LowUsePercentile = percent_rank(LowUsePerc),
                  MeanPricePercentile = percent_rank(MeanPrice)))

cor(test$LowUsePerc,test$MeanPrice,"complete.obs")
cor(test$LowUsePerc,test$MedianPrice, "complete.obs")

cor(test$LowUsePercentile,test$MeanPricePercentile , "complete.obs")

test %>%
  ggplot(aes(x= LowUsePercentile, y = MeanPricePercentile)) +geom_point()

test <-ls(pattern = "DATA") %>%
  map_dbl(~{ df <-get(.x)
    cor(df$LowUsePerc,df$MeanPrice,"complete.obs", method = "kendall")
  })

  plot(density(abs(test)))

  Combine1ExO %>%
    ggplot(., aes(x = absdiff>0 )) +geom_bar()

>>>>

BirminghamDATA <-  read_excel("Birmingham CT EMPTIES.xlsx" )%>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Current Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
  StructureData(c(2,4:9))

@@

#Mid Suffolk and Babergh
#These have been combined and are just the postcodes so need to be fixed
#Missing loads of postcodes
MidSuffolkDATA <- read_excel("MidSuffolk FOI MF379 1718 Discount.xlsx") %>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
  StructureData(c(2:12,14:15))

BaberghDATA <- read_excel("Babergh FOI BF378 1718 Discount.xlsx")%>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
  StructureData(c(2:6,8:11,13:15))

@@

@@

PlotMap(ConwyDATA)

@@

MakeLeaflet(ConwyDATA)

@@

decile %>% 
  filter(type == "Excluding London") %>% 
  ggplot(aes(x= ratio, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")

@@

data_frame(Index = 1:100) %>%
  mutate(Primary = exp(-0.05*(Index))+0.05, 
         Auxilary = (exp(Index/100)-1),
    Total = Primary + Auxilary) %>%
  gather(key = "Type", value = "value", -Index) %>%
  ggplot(aes(x= Index, y = value, colour = Type )) +
  geom_line() +
  labs(title = "LUP percentage as a function of primary and Auxilary demand",
       x = "Demand",
       y = "LUP percentage") +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank()
  )
SaveFig("TheoreticalDemand.pdf")

@@

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities")

#Find what needs to be bootstrapped
BootStrapFiles <- list.files(getwd()) %>% gsub("DATA.rds", "",.)
  newLADsnames <- sub("DATA", "", ls(pattern = "DATA", envir = globalenv())) %>% 
    .[!(. %in% BootStrapFiles)] 
  newLADs <- paste0(newLADsnames, "DATA")

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 10, type, PropertyTypes)%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

  #once all Bootratps complete load them all into a list
 BootStrapRES <- list.files(getwd()) %>%
   map(~readRDS(.x))

 #name the list
 names(BootStrapRES) <- list.files(getwd()) %>% gsub(".rds", "",.)

BootStrapRESExO <- BootStrapRES
#Should clean up and remove EXO
rm(BootStrapRES)

#Make a summary dataframe
Combine1ExO <- BootResSummaryData(BootStrapRESExO)

@@

test <- BootStrapRESExO %>% 
  bind_rows %>%
  select(-LAD11CD) %>%
  group_by(class, ID) %>%
  summarise_all(sum) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")),
               LUPmore = RatioExvsAct>1)

@@

@@

LUPval <-   map2(.x =BootStrapRESExO, .y =   names(BootStrapRESExO),~ {.x %>% mutate(LAD  = .y)}) %>%
  bind_rows %>%
  select(-class, -LAD11CD) %>%
  group_by(LAD, ID) %>%
  summarise_all(sum) %>%
  group_by(LAD) %>%
  summarise_all(mean) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
  mutate(VancouverTax = LowUseValue*0.01/1000)

#value is billions of pounds of a vancouver tax in England and wales.
LUPval$VancouverTax %>% sum(.)/1000

@@

@@

##Create modelling dataframe

@@

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent) %>% as.numeric,
         LUPdepExt = scale(LUPdepExt) %>% as.numeric,
         maxPerc = scale(maxPerc) %>% as.numeric,
         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
         price = scale(price) %>% as.numeric,
         Extent = scale(Extent) %>% as.numeric) %>%
  mutate(Reference = (HighVal>(LUPS-HighVal)) %>% as.factor)
```

##create functions to get out model preds

```{r}
 GetAccuracy <- function(df, splits , Var ) {
  select_(df,splits) %>% flatten %>%
           map2_dbl(select_(df,Var) %>% flatten, ., ~{ augment(.x, newdata = assessment(.y)) %>%
               mutate(.fitted = factor(.fitted > 0,
                        levels = as.factor(c("FALSE", "TRUE"))))  %>%
              accuracy(., Reference, .fitted)} ) }

#If this one is used on the logistic regression I get an "incorrect number of dimensions error"
GetAccuracyForest <- function(df, splits , Var ) {
   select_(df,splits) %>% flatten %>%
map2_dbl( select_(df,Var) %>% flatten, ~{assessment(.x) %>%
   mutate(fitted = predict(.y, .) %>% .[,colnames(.)=="TRUE"],
          fitted = factor(fitted > 0,
                        levels = as.factor(c("FALSE", "TRUE")))) %>%
              accuracy(., Reference, fitted) 
}) }

@@

#Create Models
```{r}

FOIFormula <- as.formula(Reference~ LUPdepExt + price + VacantsPerc)
OpenFormula <- as.formula(Reference~ Extent + price + VacantsPerc)

set.seed(4622)
Modeldf <- ModelMe  %>%
  vfold_cv(., V = 10, repeats = 100) %>%
  mutate(LogisticFOI = splits %>%
  map(.,~{ glm(FOIFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  LogisticOpen = splits %>%
  map(.,~{ glm(OpenFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  ForestOpen = splits %>% 
    map(., ~{rpart(OpenFormula, data=analysis(.x))})
  ) %>%
  mutate(LogFoiAcc = GetAccuracy(., "splits", "LogisticFOI"),
         LogOpenAcc = GetAccuracy(., "splits", "LogisticOpen"), 
         ForestOpenAcc = GetAccuracyForest(., "splits", "ForestOpen"))

Modeldf$LogisticOpen %>%
   map_df(., ~coefficients(.x) %>%
            as.data.frame(.) %>% rownames_to_column()) %>%
   setNames(c("key", "value")) %>%
  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
  labs(title = "Coefficient values across 100 samples of 10 fold cross validation")
SaveFig("ModelCoeffs.pdf")

ModComp <- Modeldf %>%
  select(LogFoiAcc, LogOpenAcc) %>%
  gather

  ModComp %>%
  ggplot(aes(x=model, y = statistic, fill = model)) + 
  geom_boxplot()

  ModComp %>%
  group_by(model) %>%
  summarise(mean =mean(statistic))

@@

#All England Bootstrap

```{r}
#Create model using all data
Mod <- ModelMe %>% 
  glm(OpenFormula, data = ., binomial(link='logit'))

@@

EnglandComp <- LADDep %>% 
  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
  left_join(., Vacants, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
  left_join( LadHomes, by = "LAD11CD") %>%
  ungroup %>%
  #left_join(Rural, by = "LAD11CD") %>%
  as.data.frame() %>%
  mutate(VacantsPerc = Vacants/Homes,
  #scaled so that the binomial can be interpreted
  pricepercent = pricepercent %>% scale %>% as.numeric,
         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
         price = scale(price) %>% as.numeric,
         Extent = scale(Extent) %>% as.numeric) %>%
  mutate(Prob = predict(Mod, newdata = ., type ="response")) %>%
  #merge on the truth
  left_join(ModelMe %>% select(LAD11CD, Reference), by = "LAD11CD") %>%
  mutate(BootCol = case_when(Reference == TRUE ~1,
                             Reference == FALSE ~ 0,
                             TRUE ~ Prob),
         Comp.Type = Prob>0.5)

BootPopHigh <-map2(EnglandComp$Pop, EnglandComp$BootCol, 
            ~sample(c(.x, 0), size = 1000, 
                    replace = TRUE,
                    prob = c(.y, 1-.y)) %>%
              as.tibble) %>%
  bind_cols() %>%
  rowSums() %>%
  tibble(Pop=.) %>%
  mutate(PercPop = Pop/sum(EnglandComp$Pop))

BootPopHigh %>%
  ggplot(aes(x = PercPop)) +
  geom_density()

#The 95 percent confidence interval of the mean
QuantInfo<-quantile(BootPopHigh$Pop, probs = c(0.05, 0.5 ,0.95))
quantile(BootPopHigh$PercPop, probs = c(0.05, 0.5 ,0.95))
#diff is 3.6M
QuantInfo[3]-QuantInfo[1]

@@

### 2018-07-17 allEnglandMap.Rmd
High value LUPS
I added in the number of LUPS that are worth more than the LAD median. This required changing BootsratpDistribcompare. However I can now predict the LADs where the majority of LUPs are high value, which is easier for people to understand.

  MyData <- EnglandComp %>%
    select(LAD11CD, Significant.Competition, LAD11NM, Comp.Type) %>%
    merge(MyData, .)

@@

  labels <- sprintf(
    "<strong>%s</strong><br/>Market affected %s",
    MyData$LAD11NM, MyData$Comp.Type
  ) %>% lapply(htmltools::HTML)

@@

>>>>

    MyData <- EnglandComp %>%
    select(LAD11CD, LAD11NM, Comp.Type) %>%
    merge(MyData, .)
  # MyData <- EnglandComp %>%
  #   select(LAD11CD, Significant.Competition, LAD11NM, Comp.Type) %>%
  #   merge(MyData, .)

@@

  labels <- sprintf(
    "<strong>%s</strong><br/>Predominantly high value LUPs %s",
    MyData$LAD11NM, MyData$Comp.Type
  ) %>% lapply(htmltools::HTML)

@@

  z
